---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data  
##### The activity.zip file has already been unpacked via the git cml

```{r}
# Loading the data
# Retrieve data and store in a dataframe called datafile

setwd("C:/Users/evdmaaten/Documents/GitHub/RepData_PeerAssessment1/activity")
datafile <- read.csv("activity.csv")

# Preprocessing the data
# Remove incomplete observations from datafile

#datafile <- datafile[complete.cases(datafile),]
```

## What is mean total number of steps taken per day?

```{r}
# Create a dataframe with the total number of steps per day

totalnumberofstepsperday <- tapply(datafile$steps, datafile$date, sum, na.rm=TRUE)
totalnumberofstepsperday <- totalnumberofstepsperday[complete.cases(totalnumberofstepsperday)]

# Create a histogram of the dataframe with the total number of steps per day

hist(totalnumberofstepsperday, breaks = 20,)

# Calculate the mean number of steps per day

mean(totalnumberofstepsperday, na.rm=TRUE)

# Calculate the median number of steps per day

median(totalnumberofstepsperday, na.rm=TRUE)
```

## What is the average daily activity pattern?

##### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
# Create a dataframe with the mean steps for each five minute interval.
FiveMinuteIntervals <- tapply(datafile$steps, datafile$interval, mean, na.rm = TRUE)
plot(FiveMinuteIntervals, type = "l")
```

##### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
which.max(FiveMinuteIntervals)
```

##### It turns out two 5-minute intervals contain the maximum number of steps

## Imputing missing values

##### Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
sum(is.na(datafile))
```
##### Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
```{r}
#create a new dataframe called imputeddatafile to fill in the NA's

imputeddatafile <- datafile

```
## Are there differences in activity patterns between weekdays and weekends?
